### 2018-10-19 algorithm.tex
free trade formulas: gamma vs gamma'
re #10: experimenting with labor share bounds

>>>>

When wages are constant across sectors, we can write expenditure shares as
\begin{equation}\label{eq:sectoral_share:2}
e_{mjt} = \frac
	{w_{mt}\sum_{k=1}^J(\alpha_{mjt}(\mathbf P_t)\beta_k+\gamma_{jk}) L_{mkt}/\beta_k - S_{mt}}
	{w_{mt}\sum_{k=1}^J L_{mkt}/\beta_k-S_{mt}}.
\end{equation}
If $S_{mt}=0$ and demand is Cobb-Douglas, this can be precalculated in the outer loop, without knowing anything about wages. The inner loop (without the need for a middle loop) then solves for prices and wages.
\[
	\varrho_{njt} = w_{nt}^{-1/\theta}(L_{njt}/\beta_j)^{-1/\theta}
	\left[
	\sum_{m=1}^N
		(\kappa_{mnjt} P_{mjt})^{\theta}
		w_{mt}\sum_{k=1}^J(\alpha_{mjt}(\mathbf P_t)+\gamma_{jk}/\beta_k) L_{mkt} - S_{mt}
	\right]^{1/\theta}.
\]
We also know that 
\begin{equation}\label{eq:varrho:2}
	\varrho_{njt} = w_{nt}^{\beta_j} \xi B_j A_{njt}^{-1}  \prod_{k=1}^J P_{nkt}^{\gamma_{kj}}.
\end{equation}
